\documentclass[a4paper]{article}
\usepackage{wasysym}
\usepackage[left = 2.0cm, top = 1.25cm, right = 2.0cm, bottom = 1.25cm]{geometry}
\usepackage{multicol}
\begin{document}
	\noindent{\Large \textbf{Akor Stanley}}\\
	 B274,Army Barracks,Effurun-Warri,Delta State,Nigeria.\\
	\textbf{Tel:}  +2348168208506\\
	\textbf{Email:} akorstanley0@gmail.com\\
	\textbf{Skype:} +23481682856\\
	\textbf{Twitter:} @akor.stanley\\
	
	\noindent\textbf{Education}
	\\
	\vspace{-2.8mm}
	\hrule 
	\vspace{2.5mm}
	
	\noindent \textbf{Plateau State ICT Department}   \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \textbf{August. 2019}\\ Certificate in Digital Skills  \\
	
	
	
	\noindent \textbf{Federal University of Petroleum Resources} \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \quad \qquad  \textbf{2015 - 2019} \\
	Bachelor of Science Physical (Physics) with first class honours\\\\
	\textbf{Work Experience}
	\\
	\vspace{-2.8mm}
	\hrule 
	\vspace{2.5mm}
	

	\noindent \textbf{University of Jos, nigeria. }  \qquad  \qquad \qquad\qquad \qquad\qquad \qquad\qquad \ \ \ \qquad \qquad \ \  \textbf{ Feb. 2019 - March. 2020} 
	\\
	 Teaching Assistant 
		\begin{multicols}{2}
		\begin{itemize}
			\item Handling Tutorials and Electronics Practicals.
			\item Weekly evaluation of students' practical reports.
		\end{itemize}
	\end{multicols}
	
	\noindent \textbf{Research Experience}
	\\
	\vspace{-2.8mm}
	\hrule 
		\vspace{2.5mm}
		
	
	\vspace{2.5mm}
	\noindent \textbf{BSc. Final year project}  \qquad \quad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \quad \quad \quad \quad \quad\quad \quad \quad \textbf{October 2018 } 
	\\
     Investigation on the Structural and Electronic Properties of half Heusler Alloys.\\
    
     
	\noindent \textbf{Intern student - Bisalo Electrical Engineering Company,Warri-Nigeria.}   \quad \textbf{April.- October. 2017} 
	
	\begin{itemize}
		\item Repair and Maintenace of Electrical Machines.
		\item Fabrication, repairing and replacing damaged street lights and electronic boxes
		\item Troubleshooting, maintaining and installation of both electric and solar street lights along the city.
		\item Maintenance of traffic lights (system integration), researching and modelling of different mechanisms on how to reduce traffic at peak hours in the city
	\end{itemize}
	
	
	\noindent \textbf{Extra-Curricular Activities}
	\\
	\vspace{-2.8mm}
	\hrule 
	\vspace{2.5mm}
	
	\noindent \textbf{Centre for Peace Advancement In Nigeria}    \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \textbf{Feb. 2019 -Present}\\ Member, Outreach Commitee.
	\begin{itemize}
		\item Organising the group for outreach programs.
		\item Reaching out to schools for a proposed visit.
		
	\end{itemize}
	
	
	\noindent \textbf{Volunteer Science Tutor}     \quad \qquad \ \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad  \quad \quad  \textbf{March - Sept. 2020} 
	\\
	\begin{itemize}
		\item Organising free academic  tutorials for high school and freshmen undergraduate students.
		\item Rendering counselling services when required.
		
	\end{itemize}
	\vspace{2.5mm}
	\noindent \textbf{FUPRE Physics Society}    \qquad  \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \qquad \quad \qquad \ \  \textbf{April. 2017 - April. 2018} 
	\\
	Vice President
	\begin{itemize}
	\item Promoting science both at lower and higher levels through outreach to schools and handling students issues
	\item Fundraising for the needy
	\item Students counselling and Guidance
	
	\end{itemize}
\newpage
		
		
		


	\noindent \textbf{Skills and competence}
	\\
	\vspace{-2.8mm}
	\hrule 
	\vspace{-3.5mm}
	\begin{multicols}{2}
		\begin{itemize}
				
		
			
			\item Computing skills, Microsoft Office, Latex
			\item Programming: Python,Ferret.
			\item Driver class B vehicles
			\item Technician 
		\end{itemize}
	\end{multicols}
   %\newpage
	\noindent \textbf{Membership}
	\\
	\vspace{-2.8mm}
	\hrule 
	%\vspace{1.5mm}
	\begin{multicols}{2}
		\begin{itemize}
			\item MPAS Group
			\item 	Nigerian Association of Physics Students.
			\item AIMS community
			\item Centre for Peace Advancement in Nigeria
			\item Agro-allied Community Development Group
		\end{itemize}
	\end{multicols}
	
	
	
	%\begin{multicols}{2}
		
	%\end{multicols}
		
	
	\noindent \textbf{Seminars Attended}
	\\
\vspace{-2.8mm}
\hrule
\vspace{3.5mm}
%\begin{multicols}{2}
\begin{itemize}
\item Graph Theory: Etremal Trees with fixed degree
 sequence
\item Pydata Conference.
			%\item 	Nigerian Association of Physics Students.
			%\item AIMS community
			%\item Centre for Peace Advancement in Nigeria
			%\item Agro-allied Community Development Group
\end{itemize}
%\end{multicols}
	



\noindent \textbf{References}
	\\
\vspace{-2.8mm}
\hrule
\vspace{3.5mm}
\noindent 	Dr. Nenuwe Nelson
\\
Federal University of Petroleum Resources\\
Senior Lecturer\\
nenuwe.nelson@fupre.edu.ng\\
\\
\noindent Olaseni Babasola Victor\\
Federal University of Petroleum Resources\\
Physics Department\\
olaseni.victor@fupre.edu.ng\\
%+256752272366\\\\


%\noindent Mohamed MBEHOU 
%\\
%University of Yaounde I\\
%Senior Lecturer\\
%mbehoumoh@gmail.com\\

%\noindent Bourgeois Gadjagboui 
%\\
%African Institute for Mathematical Sciences\\
%Tutor\\
%bourgeois@aims.edu.gh\\
%+250780914986



 \thispagestyle{empty} 

\end{document}